---
output:
  md_document:
    variant: markdown_github
---

## **tranSurv**

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/tranSurv)](https://cran.r-project.org/package=tranSurv)
[![packageversion](https://img.shields.io/badge/Package%20version-1.2.1-orange.svg?style=flat-square)](commits/master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/stc04003/tranSurv?branch=master&svg=true)](https://ci.appveyor.com/project/stc04003/tranSurv)
[![Travis-CI Build Status](https://travis-ci.org/stc04003/tranSurv.svg?branch=master)](https://travis-ci.org/stc04003/tranSurv)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

#### Transformation model for left-truncated right-censored survival data
***tranSurv*** implements methods for survival analysis under a dependent truncation and independent right censoring via a structural transformation method.
The package is still under active development.

---

A package that estimates survival curve under a dependent truncation and independent right censoring
via a structural transformation method.
The package also includes hypothesis test of quasi-independence based on the conditional Kendall's tau
of Martin and Betensky (2005) and two versions of the inverse probability weighted Kendall's tau of
Austin and Betensky (2014).

## Installation

Install and load the package from CRAN using 

```{r install, eval = FALSE}
install.packages("tranSurv")
library(tranSurv)
```

Install and load the package from GitHub using 
```{r github, eval = FALSE}
devtools::install_github("stc04003/tranSurv")
library(tranSurv)
```

### Online documentation 
[Online document](https://www.sychiou.com/tranSurv/index.html) includes:

* Package vignette on [testing quasi-independence](https://www.sychiou.com/tranSurv/articles/tranSurv-quasi-independence.html)
* Package vignette on [survival curve estimation with transformation models](https://www.sychiou.com/tranSurv/articles/tranSurv-test.html)
* Package vignette on regression with with transformation models (coming up)

